On exponential sums arising from the classical doubling method

### 2025-04-10 main.tex
Minors

\begin{corollary}
\label{cor:geoconj}
Suppose that $(\algebraicGroup{T},\theta)$ and $(\algebraicGroup{T}',\theta')$ are geometrically conjugate torus character pairs in $G$. Then $g_{\algebraicGroup{T},\rho}(\chi,\theta,\psi) = g_{\algebraicGroup{T}',\rho}(\chi,\theta',\psi)$.
\end{corollary}
\begin{proof}
Both are equal to $g_{(\rho(s_{T,\theta}))}(\psi,\chi) = g_{(\rho(s_{T',\theta'}))}(\psi,\chi)$.
\end{proof}

\begin{remark}
	The above work is not surpising as it is really a rephrasing that the eigenvalues of $\rho(s)$ are independent of conjugacy.
\end{remark}

The idea behind the proof of \Cref{lem:indep_geo_conj} is that the formula from \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters} relates $\dblVirtualJacobiSumScalar{\RTGTheta{T_H}{H}{\theta_H}}{\chi}/\RTGTheta{T_H}{H}{\theta_H}\left(1\right)$ to $g_{T,\rho}(\chi,\theta,\psi)$ for the appropriate \calvin{doubling representation} $\rho$ in the table below.

>>>>

\begin{corollary}
\label{cor:geoconj}
Suppose that $(\algebraicGroup{T},\theta)$ and $(\algebraicGroup{T}',\theta')$ are geometrically conjugate torus character pairs in $G$. Then $g_{\algebraicGroup{T},\rho}(\chi,\theta,\psi) = g_{\algebraicGroup{T}',\rho}(\chi,\theta',\psi)$.
\end{corollary}
\begin{proof}
Both are equal to $$g_{(\rho(s_{T,\theta}))}\left(\chi, \fieldCharacter\right) = g_{(\rho(s_{T',\theta'}))}\left(\chi, \fieldCharacter\right).$$
\end{proof}

\begin{remark}
	The above work is not surprising as it is really a rephrasing that the eigenvalues of $\rho(s)$ are independent of conjugacy.
\end{remark}

The idea behind the proof of \Cref{lem:indep_geo_conj} is that the formula from \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters} relates $\dblVirtualJacobiSumScalar{\RTGTheta{T_H}{H}{\theta_H}}{\chi}/\RTGTheta{T_H}{H}{\theta_H}\left(1\right)$ to $g_{T,\rho}(\chi,\theta,\psi)$ for the appropriate standard representation $\rho$ in the table below.
